---
title: "Modern paramaterization"
author: "Jen Baron"
date: "January 10, 2022"
output:
  html_document:
    keep_md: yes
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: "hide"
---

```{r include = FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
```

# Load Packages

```{r}
library(dplyr)
library(ggplot2)
```

# Read Data

Polygon data from BEC subzones intersected with PEM aspect (warm/cool).

```{r}
Columbia_Area <- read.csv("data/BEC_PEM_Columbia.csv")
Elk_Area <- read.csv("data/BEC_PEM_Elk.csv")
KootenayN_Area <- read.csv("data/BEC_PEM_Kootenay_North.csv")
KootenayS_Area <- read.csv("data/BEC_PEM_Kootenay_South.csv")
Purcell_Area <- read.csv("data/BEC_PEM_Purcell.csv")
```

Polygon data from BEC subzones intersected with PEM aspect (warm/cool), with non-fuels removed using the BCWS Fire Fuel Types dataset. 

```{r}
Columbia_Fuel <- read.csv("data/BEC_PEM_Columbia_Fuel.csv")
Elk_Fuel <- read.csv("data/BEC_PEM_Elk_Fuel.csv")
KootenayN_Fuel <- read.csv("data/BEC_PEM_Kootenay_North_Fuel.csv")
KootenayS_Fuel <- read.csv("data/BEC_PEM_Kootenay_South_Fuel.csv")
Purcell_Fuel <- read.csv("data/BEC_PEM_Purcell_Fuel.csv")
```

Fire perimeters intersected with BEC subzone and PEM aspect. Contains BEC information for within fire events. Selecting only fire events after 1940. 

```{r}
Columbia_Fire <- read.csv("data/BEC_Fire_Columbia.csv") %>%
  filter(FIRE_YEAR >= 1940, Calculate_Size_Ha > 0, SIZE_HA > 0)
Elk_Fire <- read.csv("data/BEC_Fire_Elk.csv") %>%
  filter(FIRE_YEAR >= 1940, Calculate_Size_Ha > 0, SIZE_HA > 0)
KootenayN_Fire <- read.csv("data/BEC_Fire_Kootenay_North.csv") %>%
  filter(FIRE_YEAR >= 1940, Calculate_Size_Ha > 0, SIZE_HA > 0)
KootenayS_Fire <- read.csv("data/BEC_Fire_Kootenay_South.csv") %>%
  filter(FIRE_YEAR >= 1940)
Purcell_Fire <- read.csv("data/BEC_Fire_Purcell.csv") %>%
  filter(FIRE_YEAR >= 1940, Calculate_Size_Ha > 0, SIZE_HA > 0)
```

# Calculate Fire Attributes

## Subzone & Aspect

Most fire events occur across multiple BEC subzones. The original fire size characterizes fire across multiple zones. I also calculated the area of the fire within each BEC subzone which is described by the BEC summaries (as opposed to the original sizes)

```{r}
Columbia_Modern <- Columbia_Fire %>% 
  group_by(MAP_LABEL, fire_group) %>%
  summarize(number_fires = n_distinct(FIRELABEL), #number of unique fire events based on fire label
            mean_fs = mean(SIZE_HA) %>% round(2), 
            mean_fs_BEC = mean(Calculate_Size_Ha) %>% round(2),
            min_fs = min(SIZE_HA) %>% round(2),
            min_fs_BEC = min(Calculate_Size_Ha) %>% round(2),
            max_fs = max(SIZE_HA) %>% round(2),
            max_fs_BEC = max(Calculate_Size_Ha) %>% round(2),
            area_burned = sum(SIZE_HA) %>% round(2),
            area_burned_BEC = sum(Calculate_Size_Ha) %>% round(2))
Elk_Modern <- Elk_Fire %>% 
  group_by(MAP_LABEL, fire_group) %>%
  summarize(number_fires = n_distinct(FIRELABEL), 
            mean_fs = mean(SIZE_HA) %>% round(2), 
            mean_fs_BEC = mean(Calculate_Size_Ha) %>% round(2),
            min_fs = min(SIZE_HA) %>% round(2),
            min_fs_BEC = min(Calculate_Size_Ha) %>% round(2),
            max_fs = max(SIZE_HA) %>% round(2),
            max_fs_BEC = max(Calculate_Size_Ha) %>% round(2),
            area_burned = sum(SIZE_HA) %>% round(2),
            area_burned_BEC = sum(Calculate_Size_Ha) %>% round(2))
KootenayN_Modern <- KootenayN_Fire %>% 
  group_by(MAP_LABEL, fire_group) %>%
  summarize(number_fires = n_distinct(FIRELABEL), #number of unique fire events based on fire label
            mean_fs = mean(SIZE_HA) %>% round(2), 
            mean_fs_BEC = mean(Calculate_Size_Ha) %>% round(2),
            min_fs = min(SIZE_HA) %>% round(2),
            min_fs_BEC = min(Calculate_Size_Ha) %>% round(2),
            max_fs = max(SIZE_HA) %>% round(2),
            max_fs_BEC = max(Calculate_Size_Ha) %>% round(2),
            area_burned = sum(SIZE_HA) %>% round(2),
            area_burned_BEC = sum(Calculate_Size_Ha) %>% round(2))
KootenayS_Modern <- KootenayS_Fire %>% 
  group_by(MAP_LABEL, fire_group) %>%
  summarize(number_fires = n_distinct(FIRELABEL), #number of unique fire events based on fire label
            mean_fs = mean(SIZE_HA) %>% round(2), 
            mean_fs_BEC = mean(Calculate_Size_Ha) %>% round(2),
            min_fs = min(SIZE_HA) %>% round(2),
            min_fs_BEC = min(Calculate_Size_Ha) %>% round(2),
            max_fs = max(SIZE_HA) %>% round(2),
            max_fs_BEC = max(Calculate_Size_Ha) %>% round(2),
            area_burned = sum(SIZE_HA) %>% round(2),
            area_burned_BEC = sum(Calculate_Size_Ha) %>% round(2))
Purcell_Modern <- Purcell_Fire %>% 
  group_by(MAP_LABEL, fire_group) %>%
  summarize(number_fires = n_distinct(FIRELABEL), #number of unique fire events based on fire label
            mean_fs = mean(SIZE_HA) %>% round(2), 
            mean_fs_BEC = mean(Calculate_Size_Ha) %>% round(2),
            min_fs = min(SIZE_HA) %>% round(2),
            min_fs_BEC = min(Calculate_Size_Ha) %>% round(2),
            max_fs = max(SIZE_HA) %>% round(2),
            max_fs_BEC = max(Calculate_Size_Ha) %>% round(2),
            area_burned = sum(SIZE_HA) %>% round(2),
            area_burned_BEC = sum(Calculate_Size_Ha) %>% round(2))
```
### Fire Rotation Interval

$FRI = \frac {(Year_2 - Year_1)} {\frac{Area Burned} {Total Area}}$



Calculate flammable area in each BEC subzone/aspect for FRI calculation
```{r}
Columbia_Fuel_Area <- Columbia_Fuel %>% 
  group_by(MAP_LABEL, fire_group) %>%
  summarize(total_area = sum(Calculate_Area_Ha) %>% round(2)) 
Elk_Fuel_Area <- Elk_Fuel %>% 
  group_by(MAP_LABEL, fire_group) %>%
  summarize(total_area = sum(Calculate_Area_Ha) %>% round(2)) 
KootenayN_Fuel_Area <- KootenayN_Fuel %>% 
  group_by(MAP_LABEL, fire_group) %>%
  summarize(total_area = sum(Calculate_Area_Ha) %>% round(2)) 
KootenayS_Fuel_Area <- KootenayS_Fuel %>% 
  group_by(MAP_LABEL, fire_group) %>%
  summarize(total_area = sum(Calculate_Area_Ha) %>% round(2)) 
Purcell_Fuel_Area <- Purcell_Fuel %>% 
  group_by(MAP_LABEL, fire_group) %>%
  summarize(total_area = sum(Calculate_Area_Ha) %>% round(2)) 
```

```{r}
years = (2020-1940+1) # Time period for fire events

Columbia_Modern <- full_join(Columbia_Modern, Columbia_Fuel_Area) %>%
  mutate(FRI.percent = (area_burned_BEC/total_area)*100 %>% round(2),
         FRI = years / (area_burned_BEC/total_area) %>% round(2),
         Region = "Columbia")
Elk_Modern <- full_join(Elk_Modern, Elk_Fuel_Area) %>%
  mutate(FRI.percent = (area_burned_BEC/total_area)*100 %>% round(2),
         FRI = years / (area_burned_BEC/total_area) %>% round(2),
          Region = "Elk")
KootenayN_Modern <- full_join(KootenayN_Modern, KootenayN_Fuel_Area) %>%
  mutate(FRI.percent = (area_burned_BEC/total_area)*100 %>% round(2),
         FRI = years / (area_burned_BEC/total_area) %>% round(2),
         Region = "Kootenay North")
KootenayS_Modern <- full_join(KootenayS_Modern, KootenayS_Fuel_Area) %>%
  mutate(FRI.percent = (area_burned_BEC/total_area)*100 %>% round(2),
         FRI = years / (area_burned_BEC/total_area) %>% round(2),
         Region = "Kootenay South")
Purcell_Modern <- full_join(Purcell_Modern, Purcell_Fuel_Area) %>%
  mutate(FRI.percent = (area_burned_BEC/total_area)*100 %>% round(2),
         FRI = years / (area_burned_BEC/total_area) %>% round(2),
         Region = "Purcell")

Modern <- rbind(Columbia_Modern, Elk_Modern, KootenayN_Modern, KootenayS_Modern, Purcell_Modern) %>%
  ungroup() %>%
  rename(Zone = Region, Region_Name = MAP_LABEL, Aspect = fire_group) %>%
  select(Zone, Region_Name, Aspect, number_fires, mean_fs_BEC, min_fs_BEC, max_fs_BEC, FRI) %>%
  relocate(Zone, Region_Name, Aspect) %>%
  mutate_if(is.character,as.factor) %>%
  mutate_if(is.numeric, round, 0)

Modern$FRI <- Modern$FRI %>% na_if(Inf) #convert infinite FRI values to NA
```
 
### Visualize

```{r}
ggplot(data=Modern, aes(x=Region_Name, y=number_fires)) +
  geom_col(stat="identity", position = "dodge", aes(fill=Aspect)) +
  scale_fill_manual(values=c("lightblue2", "lightpink2")) +
  labs(x = "") +
  facet_grid(Zone~., scales="free_y") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))

ggplot(data=Modern, aes(x=Region_Name, y=mean_fs_BEC)) +
  geom_col(stat="identity", position = "dodge", aes(fill=Aspect)) +
  scale_fill_manual(values=c("lightblue2", "lightpink2")) +
  facet_grid(Zone~., scales="free_y") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))

ggplot(data=Modern, aes(x=Region_Name, y=min_fs_BEC)) +
  geom_col(stat="identity", position = "dodge", aes(fill=Aspect)) +
  scale_fill_manual(values=c("lightblue2", "lightpink2")) +
  facet_grid(Zone~., scales="free_y") +
  labs(x = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))

ggplot(data=Modern, aes(x=Region_Name, y=max_fs_BEC)) +
  geom_col(stat="identity", position = "dodge", aes(fill=Aspect)) +
  scale_fill_manual(values=c("lightblue2", "lightpink2")) +
  facet_grid(Zone~., scales="free_y") +
  labs(x = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))

ggplot(data=Modern, aes(x=Region_Name, y=FRI)) +
  geom_col(stat="identity", position = "dodge", aes(fill=Aspect)) +
  scale_fill_manual(values=c("lightblue2", "lightpink2")) +
  facet_grid(Zone~., scales="free_y") +
  labs(x = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))
```


```{r}
ggplot(data = Modern, aes(x=Zone, y =number_fires, fill=Aspect)) +
  geom_boxplot(outlier.shape=NA) +
  geom_point(pch=21,position = position_jitterdodge(), size=0.8, alpha=0.5, stroke=1) +
  scale_fill_manual(values=c("lightblue2", "lightpink2")) +
  theme_bw() +
  labs(y= "Number of Fires", x = "") +
  theme(axis.text.x = element_text(angle = 90))

ggplot(data = Modern, aes(x=Zone, y =mean_fs_BEC, fill=Aspect)) +
  geom_boxplot(outlier.shape=NA) +
  geom_point(pch=21,position = position_jitterdodge(), size=0.8, alpha=0.5, stroke=1) +
  scale_fill_manual(values=c("lightblue2", "lightpink2")) +
  theme_bw() +
  labs(y= "Mean Fire Size (ha)", x = "") +
  theme(axis.text.x = element_text(angle = 90))

ggplot(data = Modern, aes(x=Zone, y =min_fs_BEC, fill=Aspect)) +
  geom_boxplot(outlier.shape=NA) +
  geom_point(pch=21,position = position_jitterdodge(), size=0.8, alpha=0.5, stroke=1) +
  scale_fill_manual(values=c("lightblue2", "lightpink2")) +
  theme_bw() +
  labs(y= "Minimum Fire Size (ha)", x = "") +
  theme(axis.text.x = element_text(angle = 90))

ggplot(data = Modern, aes(x=Zone, y =max_fs_BEC, fill=Aspect)) +
  geom_boxplot(outlier.shape=NA) +
  geom_point(pch=21,position = position_jitterdodge(), size=0.8, alpha=0.5, stroke=1) +
  scale_fill_manual(values=c("lightblue2", "lightpink2")) +
  theme_bw() +
  labs(y= "Maximum Fire Size (ha)", x = "") +
  theme(axis.text.x = element_text(angle = 90))

ggplot(data = Modern, aes(x=Zone, y =FRI, fill=Aspect)) +
  geom_boxplot(outlier.shape=NA) +
  geom_point(pch=21,position = position_jitterdodge(), size=0.8, alpha=0.5, stroke=1) +
  scale_fill_manual(values=c("lightblue2", "lightpink2")) +
  theme_bw() +
  labs(y= "Fire Rotation Interval (years)", x = "") +
  expand_limits(y=10000) +
  theme(axis.text.x = element_text(angle = 90))
```

## Subzone


```{r}
Columbia_Fuel2 <- read.csv("data/BEC_Fuel_Columbia.csv")
Elk_Fuel2 <- read.csv("data/BEC_Fuel_Elk.csv")
KootenayN_Fuel2 <- read.csv("data/BEC_Fuel_Kootenay_North.csv")
KootenayS_Fuel2 <- read.csv("data/BEC_Fuel_Kootenay_South.csv")
Purcell_Fuel2 <- read.csv("data/BEC_Fuel_Purcell.csv")

Columbia_Fire2 <- read.csv("data/BEC_Fire_Subzone_Columbia.csv") %>%
  filter(FIRE_YEAR >= 1940, Calculate_Size_Ha > 0, SIZE_HA > 0)
Elk_Fire2 <- read.csv("data/BEC_Fire_Subzone_Elk.csv") %>%
  filter(FIRE_YEAR >= 1940, Calculate_Size_Ha > 0, SIZE_HA > 0)
KootenayN_Fire2 <- read.csv("data/BEC_Fire_Subzone_Kootenay_North.csv") %>%
  filter(FIRE_YEAR >= 1940, Calculate_Size_Ha > 0, SIZE_HA > 0)
KootenayS_Fire2 <- read.csv("data/BEC_Fire_Subzone_Kootenay_South.csv") %>%
  filter(FIRE_YEAR >= 1940)
Purcell_Fire2 <- read.csv("data/BEC_Fire_Subzone_Purcell.csv") %>%
  filter(FIRE_YEAR >= 1940, Calculate_Size_Ha > 0, SIZE_HA > 0)
```


```{r}
Columbia_Modern2 <- Columbia_Fire2 %>% 
  group_by(MAP_LABEL) %>%
  summarize(number_fires = n_distinct(FIRELABEL), #number of unique fire events based on fire label
            mean_fs = mean(SIZE_HA) %>% round(2), 
            mean_fs_BEC = mean(Calculate_Size_Ha) %>% round(2),
            min_fs = min(SIZE_HA) %>% round(2),
            min_fs_BEC = min(Calculate_Size_Ha) %>% round(2),
            max_fs = max(SIZE_HA) %>% round(2),
            max_fs_BEC = max(Calculate_Size_Ha) %>% round(2),
            area_burned = sum(SIZE_HA) %>% round(2),
            area_burned_BEC = sum(Calculate_Size_Ha) %>% round(2))
Elk_Modern2 <- Elk_Fire2 %>% 
  group_by(MAP_LABEL) %>%
  summarize(number_fires = n_distinct(FIRELABEL), 
            mean_fs = mean(SIZE_HA) %>% round(2), 
            mean_fs_BEC = mean(Calculate_Size_Ha) %>% round(2),
            min_fs = min(SIZE_HA) %>% round(2),
            min_fs_BEC = min(Calculate_Size_Ha) %>% round(2),
            max_fs = max(SIZE_HA) %>% round(2),
            max_fs_BEC = max(Calculate_Size_Ha) %>% round(2),
            area_burned = sum(SIZE_HA) %>% round(2),
            area_burned_BEC = sum(Calculate_Size_Ha) %>% round(2))
KootenayN_Modern2 <- KootenayN_Fire2 %>% 
  group_by(MAP_LABEL) %>%
  summarize(number_fires = n_distinct(FIRELABEL), 
            mean_fs = mean(SIZE_HA) %>% round(2), 
            mean_fs_BEC = mean(Calculate_Size_Ha) %>% round(2),
            min_fs = min(SIZE_HA) %>% round(2),
            min_fs_BEC = min(Calculate_Size_Ha) %>% round(2),
            max_fs = max(SIZE_HA) %>% round(2),
            max_fs_BEC = max(Calculate_Size_Ha) %>% round(2),
            area_burned = sum(SIZE_HA) %>% round(2),
            area_burned_BEC = sum(Calculate_Size_Ha) %>% round(2))
KootenayS_Modern2 <- KootenayS_Fire2 %>% 
  group_by(MAP_LABEL) %>%
  summarize(number_fires = n_distinct(FIRELABEL), 
            mean_fs = mean(SIZE_HA) %>% round(2), 
            mean_fs_BEC = mean(Calculate_Size_Ha) %>% round(2),
            min_fs = min(SIZE_HA) %>% round(2),
            min_fs_BEC = min(Calculate_Size_Ha) %>% round(2),
            max_fs = max(SIZE_HA) %>% round(2),
            max_fs_BEC = max(Calculate_Size_Ha) %>% round(2),
            area_burned = sum(SIZE_HA) %>% round(2),
            area_burned_BEC = sum(Calculate_Size_Ha) %>% round(2))
Purcell_Modern2 <- Purcell_Fire2 %>% 
  group_by(MAP_LABEL) %>%
  summarize(number_fires = n_distinct(FIRELABEL), 
            mean_fs = mean(SIZE_HA) %>% round(2), 
            mean_fs_BEC = mean(Calculate_Size_Ha) %>% round(2),
            min_fs = min(SIZE_HA) %>% round(2),
            min_fs_BEC = min(Calculate_Size_Ha) %>% round(2),
            max_fs = max(SIZE_HA) %>% round(2),
            max_fs_BEC = max(Calculate_Size_Ha) %>% round(2),
            area_burned = sum(SIZE_HA) %>% round(2),
            area_burned_BEC = sum(Calculate_Size_Ha) %>% round(2))
```


### Fire Rotation Interval

Calculate flammable area in each BEC subzone for FRI calculation

```{r}
Columbia_Fuel_Area2 <- Columbia_Fuel2 %>% 
  group_by(MAP_LABEL) %>%
  summarize(total_area = sum(Calculate_Area_Ha) %>% round(2)) 
Elk_Fuel_Area2 <- Elk_Fuel2 %>% 
  group_by(MAP_LABEL) %>%
  summarize(total_area = sum(Calculate_Area_Ha) %>% round(2)) 
KootenayN_Fuel_Area2 <- KootenayN_Fuel2 %>% 
  group_by(MAP_LABEL) %>%
  summarize(total_area = sum(Calculate_Area_Ha) %>% round(2)) 
KootenayS_Fuel_Area2 <- KootenayS_Fuel2 %>% 
  group_by(MAP_LABEL) %>%
  summarize(total_area = sum(Calculate_Area_Ha) %>% round(2)) 
Purcell_Fuel_Area2 <- Purcell_Fuel2 %>% 
  group_by(MAP_LABEL) %>%
  summarize(total_area = sum(Calculate_Area_Ha) %>% round(2)) 
```


```{r}
years = (2020-1940+1) # Time period for fire events

Columbia_Modern2 <- full_join(Columbia_Modern2, Columbia_Fuel_Area2) %>%
  mutate(FRI.percent = (area_burned_BEC/total_area)*100 %>% round(0),
         FRI = years / (area_burned_BEC/total_area) %>% round(2),
         Region = "Columbia")
Elk_Modern2 <- full_join(Elk_Modern2, Elk_Fuel_Area2) %>%
  mutate(FRI.percent = (area_burned_BEC/total_area)*100 %>% round(2),
         FRI = years / (area_burned_BEC/total_area) %>% round(2),
          Region = "Elk")
KootenayN_Modern2 <- full_join(KootenayN_Modern2, KootenayN_Fuel_Area2) %>%
  mutate(FRI.percent = (area_burned_BEC/total_area)*100 %>% round(2),
         FRI = years / (area_burned_BEC/total_area) %>% round(2),
         Region = "Kootenay North")
KootenayS_Modern2 <- full_join(KootenayS_Modern2, KootenayS_Fuel_Area2) %>%
  mutate(FRI.percent = (area_burned_BEC/total_area)*100 %>% round(2),
         FRI = years / (area_burned_BEC/total_area) %>% round(2),
         Region = "Kootenay South")
Purcell_Modern2 <- full_join(Purcell_Modern2, Purcell_Fuel_Area2) %>%
  mutate(FRI.percent = (area_burned_BEC/total_area)*100 %>% round(2),
         FRI = years / (area_burned_BEC/total_area) %>% round(2),
         Region = "Purcell")

Modern2 <- rbind(Columbia_Modern2, Elk_Modern2, KootenayN_Modern2, KootenayS_Modern2, Purcell_Modern2) %>%
  ungroup() %>%
  rename(Zone = Region, Region_Name = MAP_LABEL) %>%
  select(Zone, Region_Name, number_fires, mean_fs_BEC, min_fs_BEC, max_fs_BEC, FRI) %>%
  relocate(Zone, Region_Name) %>%
  mutate_if(is.character,as.factor) %>%
  mutate_if(is.numeric, round, 0)

Modern2$FRI <- Modern2$FRI %>% na_if(Inf) #convert infinite FRI values to NA

```

### Visualize

```{r}
ggplot(data=Modern2, aes(x=Region_Name, y=number_fires)) +
  geom_col(stat="identity", position = "dodge") +
  labs(x = "") +
  facet_grid(Zone~., scales="free_y") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))

ggplot(data=Modern2, aes(x=Region_Name, y=mean_fs_BEC)) +
  geom_col(stat="identity", position = "dodge") +
  facet_grid(Zone~., scales="free_y") +  labs(x = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))

ggplot(data=Modern2, aes(x=Region_Name, y=min_fs_BEC)) +
  geom_col(stat="identity", position = "dodge") +
  facet_grid(Zone~., scales="free_y") +  
  labs(x = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))

ggplot(data=Modern2, aes(x=Region_Name, y=max_fs_BEC)) +
  geom_col(stat="identity", position = "dodge") +
  facet_grid(Zone~., scales="free_y") +
  labs(x = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))


ggplot(data=Modern2, aes(x=Region_Name, y=FRI)) +
  geom_col(stat="identity", position = "dodge") +
  scale_fill_manual(values=c("lightpink2", "lightblue2")) +
  facet_grid(Zone~., scales="free_y") +
  labs(x = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))
```

```{r}
ggplot(data = Modern2, aes(x=Zone, y = number_fires)) +
  geom_boxplot(outlier.shape=NA) +
  geom_jitter(size=1, alpha=0.5) +
  labs(y= "Number of Fires", x = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))

ggplot(data = Modern2, aes(x=Zone, y =mean_fs_BEC)) +
  geom_boxplot(outlier.shape=NA) +
  geom_jitter(size=1, alpha=0.5) +
  labs(y= "Mean Fire Size (ha)", x = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))

ggplot(data = Modern2, aes(x=Zone, y =min_fs_BEC)) +
  geom_boxplot(outlier.shape=NA) +
  geom_jitter(size=1, alpha=0.5) +
  labs(y= "Minimum Fire Size (ha)", x = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))

ggplot(data = Modern2, aes(x=Zone, y =max_fs_BEC)) +
  geom_boxplot(outlier.shape=NA) +
  geom_jitter(size=1, alpha=0.5) +
  labs(y= "Maximum Fire Size (ha)", x = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))

ggplot(data = Modern2, aes(x=Zone, y =FRI)) +
  geom_boxplot(outlier.shape=NA) +
  geom_jitter(size=1, alpha=0.5) +
  labs(y= "Fire Rotation Interval (years)", x = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))
```

# Combine

```{r}
Modern_Tidy <- full_join(Modern, Modern2, 
          by=c("Zone","Region_Name"),
          suffix = c(".aspect", ""),) %>% 
  select(Zone, Region_Name, Aspect, 
                             number_fires, number_fires.aspect,
                             mean_fs_BEC, mean_fs_BEC.aspect,
                             min_fs_BEC, min_fs_BEC.aspect,
                             max_fs_BEC, max_fs_BEC.aspect,
                             FRI, FRI.aspect) %>%
  relocate(Zone, Region_Name, Aspect, 
                             number_fires, number_fires.aspect,
                             mean_fs_BEC, mean_fs_BEC.aspect,
                             min_fs_BEC, min_fs_BEC.aspect,
                             max_fs_BEC, max_fs_BEC.aspect,
                             FRI, FRI.aspect) %>%
  ungroup() %>%
  mutate_if(is.character,as.factor) %>%
  mutate_if(is.numeric, round, 0)
```


# Save Outputs

```{r}
write.csv(Modern, "outputs/modern_subzone_aspect.csv")
write.csv(Modern2, "outputs/modern_subzone.csv")
write.csv(Modern_Tidy, "outputs/modern.csv")
```


# Reproducibility

```{r}
Sys.time()
git2r::repository()
sessionInfo()
```
